### 2020-10-28 EPA:Census Team/Alison_Sociodemographic_Visualizations/Social_Demo_Chars_tidycensus.Rmd
Update Social_Demo_Chars_tidycensus.Rmd

```{r}
acs5_2018_vars <- load_variables(2018, "acs5", cache = TRUE)

view(acs5_2018_vars)
```

```{r}
sex_age_vector <- acs5_2018_vars %>%
  select(name) %>%
  slice(5:51)
```

```{r}
MI_sex_age_acs5_2018 <- get_acs(geography = "place",
              variables = c(sex_age_vector),
              state = "MI",
              year = 2018)

view(MI_sex_age_acs5_2018)
```

>>>>

```{r}
acs5_2018_vars <- load_variables(2018, "acs5", cache = TRUE)
```

```{r}
sex_age_vars <- acs5_2018_vars %>%
  slice(5:51)

sex_age_vec <- sex_age_vars %>%
  select(name) %>%
  unlist()

sex_age_label <- sex_age_vars %>%
  select(label) %>%
  unlist()
```

```{r, message = FALSE}
MI_sex_age_acs5_2018 <- get_acs(geography = "place",
              variables = sex_age_vec,
              place = "Manistee",
              state = "MI",
              year = 2018)

Manistee_sex_age_acs5_2018 <- MI_sex_age_acs5_2018 %>%
  slice(18425:18471) %>%
  mutate(sex_age_label = sex_age_label) %>%
  select(sex_age_label, estimate)
```
